---
title: ""
---

&nbsp;

### **Financial Data Analysis and Visualization in Python**

Welcome to the course website for FM 5990 - Spring 2019.

&nbsp;

```{r, loading_packages, include=FALSE}
library(fOptions)
library(bizdays)
library(tidyverse)
library(gridExtra)
```



```{r, services_art, echo=FALSE, fig.height=3.25, fig.width=8, fig.align="center"}
df_market_history <- 
    read_csv("practice_market_history.csv", col_types = cols())

df_liquidity <-
  df_market_history %>% 
    group_by(underlying) %>% 
    summarize(daily_volume = (sum(volume) / nrow(df_market_history %>% distinct(trade_date)))
              ,avg_spread = mean(ask - bid)) %>% 
    arrange(desc(daily_volume))


# let's reproduce this graph using ggplot()
p1 <- 
  ggplot(data = df_liquidity) +
  geom_point(mapping = aes(x = log(daily_volume), y = avg_spread, color="grey37"), size = 0.75, na.rm = TRUE) +
  geom_smooth(mapping = aes(x = log(daily_volume), y = avg_spread), color="steelblue1", se = FALSE, method = "loess", na.rm = TRUE) +
  scale_y_continuous(limits = c(0, 0.2)) +
  theme(axis.title.x=element_blank()
        , axis.text.x=element_blank()
        , axis.ticks.x=element_blank()
        , axis.title.y=element_blank()
        , axis.text.y=element_blank()
        , axis.ticks.y=element_blank()
        , legend.position="none"
  )


df_spy_time <-
  df_market_history %>% 
    filter(underlying == "SPY") %>%
    filter(expiration == as.Date("2013-09-21")) %>% 
    arrange(trade_date, strike)


# log-strike, like a boss
p2 <- 
    ggplot(data = df_spy_time %>% filter(trade_date < as.Date("2013-09-01"))) +
    geom_line(
        mapping = aes(x = log(strike/implied_forward)
        , y = implied_vol, group = trade_date, color = trade_date)
        , size = 0.75
        , alpha = 0.65
    ) +
  theme(axis.title.x=element_blank()
        , axis.text.x=element_blank()
        , axis.ticks.x=element_blank()
        , axis.title.y=element_blank()
        , axis.text.y=element_blank()
        , axis.ticks.y=element_blank()
        , legend.position="none"
  )

gridExtra::grid.arrange(suppressWarnings(p1), p2, nrow = 1)
```

&nbsp;

### Announcements

##### 3/4/2019
- Project page has been added.  Please e-mail me your group members so you can be assigned your underlying.

##### 2/26/2019

- Slides 04 have been added

##### 2/21/2019

- Exercises 06 and 07 have been added.

##### 2/19/2019

- Added a page called *Reading* that details all books and reading assignments for the course in chronological order.

